\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[blue]{classic}
\usepackage[utf8]{inputenc}  %Windows

%\usepackage[scale=0.975]{geometry}
\usepackage[top=0.5cm, bottom=0.5cm, left=0.5cm, right=0.5cm]{geometry}
\usepackage{graphicx}

\firstname{David}
\familyname{Valenciano}
\title{Front-End Developer}
\address{C/Isla de la Toja}{Nº1 esc D 3ºD}
\mobile{+34 600 80 90 24}
%\phone{}
%\fax{Votre Fax}
\email{david.valenciano.esteban@gmail.com}
\extrainfo{}
%\photo[50pt]{photo.png}
\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\usepackage{multibib}
\newcites{book,misc}{{Books},{Others}}

\nopagenumbers{}
\begin{document}
    \maketitle
    \section{Experience}

    \cventry{Aug 2022-- Currently }{Shopery SL}{Front-end Engineer }{}{Developed projects:}
    {\begin{itemize}
         \item Mustang, Web App development. Used technologies: HTML5, SCSS, React.js, Next.js, Typescript.
         \item YouPop, Web App development. Used technologies: HTML5, SCSS, React.js, Next.js, Typescript.
    \end{itemize}
    }
    \cventry{Sept 2021-- Aug 2022 }{Stack and Vault SL}{Front-end Engineer }{}{Developed projects:}
    {\begin{itemize}
         \item Wotoch, Web App development. Used technologies: Svelte, TypeScript.
         \item Voting Manager, Web App and Mobile development. Used technologies: HTML 5, SCSS, React.js, React Native, TypesSript.
         \item VR Manager, Web App development. Used technologies: HTML 5, SCSS, React.js, TypesSript.
         \item InmmoScout24, Web App development. Used technologies: HTML 5, SCSS, React.js, TypesSript, Redux.
    \end{itemize}
    }
    \cventry{Oct 2019-- Sept 2021 }{Capitole Consulting}{Programmer Analyst}{}{Developed projects:}
    {\begin{itemize}
         \item OWA, Web App development. Used technologies: HTML 5, SCSS, React.js, Redux, GraphQL.
    \end{itemize}
    }

    \cventry{Feb 2017-- Oct 2019 }{QUO Health SL}{Front-end Developer}{}{Developed projects:}
    {\begin{itemize}
         \item gluQUO Diabetes Academy, Web App development. Used technologies: HTML 5, SCSS, Bootstrap, React.js, Redux, React Native, Firebase.
         \item O.K Transport. Web App development. Used technologies: HTML 5, CSS 3, Bootstrap, React.js, Redux, Node.js, MongoDB, LoopBack.
         \item gluQUO PRO. Web App development. Used technologies: HTML 5, CSS 3, Bootstrap, React.js, Redux, Node.js, Firebase
         \item Optima cc web. Layout and website development. Used technologies: HTML 5, CSS 3, Bootstrap, React.js
         \item gluQUO web. Layout and website development. Used technologies: HTML 5, CSS 3, Bootstrap, React.js.
         \item QUO Health web. Design, layout and website development. Used technologies: HTML 5, CSS 3, Bootstrap, JQuery
    \end{itemize}
    }
    \cventry{2016}{Freelance}{Front-end Developer}{}{Developed projects:}
    {
        \begin{itemize}
            \item Design, layout and website development. Used technologies: HTML 5, CSS 3, Bootstrap, JQuery
        \end{itemize}
        \begin{itemize}
            \item Design, layout and website development. Used technologies: HTML 5, CSS 3, Bootstrap, JQuery
        \end{itemize}
    }
    \cventry{Sep 2015 -- Jul 2016}{HM Hospitals (Montepríncipe)}{IT CAU}{}{Developed tasks:}{
        \begin{itemize}
            \item Maintenance and incident management.
        \end{itemize}
        \begin{itemize}
            \item Development and implementation of infrastructure.
        \end{itemize}
    }

    \section{Techs}
    \cvline{}{HTML 5, CSS 3, Bootstrap, JavaScript, Typescript, Express, Node.js, React.js, Next.js, Redux, React native, Apache, MongoDB, Git, Cross-browser compatibility, Firebase, Material-UI}

    \section{Education}
    \cventry{Currently}{HND in Multiplatform Application Development}{}{Ilerna}{Online}{}
    \cventry{2020}{HND in Web Application Development}{}{Ilerna}{Online}{}
    \cventry{2017}{HND in Computer Systems and Networks Administration}{}{IES Lázaro Cárdenas}{Collado Villalba}{}
    \cventry{2015}{HND in Microcomputer Systems and Networks Technician}{}{IES Infanta Elena}{Galapagar}{}

\end{document}
